\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black} 

% margins
\usepackage[scale=0.9]{geometry}

\usepackage{datetime}
\def\dates[#1-#2 #3-#4]{\yearabove{\monthname[#2]}{#1}--\yearabove{\monthname[#4]}{#3}}
\def\datespresent[#1-#2]{\yearabove{\monthname[#2]}{#1}-- Present}
\newcommand{\yearabove}[2]{\parbox[t]{10mm}{\centering{#2\par\vspace{-2mm} \tiny{#1}}}}

\setlength{\hintscolumnwidth}{3cm} % change the width of the column with the dates

\setlength{\hintscolumnwidth}{2.6cm}

\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    \ifthenelse{\equal{#3}{}}{}{\textbf{#3}}%
    \ifthenelse{\equal{#4}{}}{}{ - \normalfont{#4}}%
    \ifthenelse{\equal{#5}{}}{}{ \normalfont{#5}}%
    \ifthenelse{\equal{#6}{}}{}{ #6}%
    \strut%
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\name{Andrew}{Rabert}
\address{PA, United States}
\phone[mobile]{(484)~601~2157}
\email{ar@nullsum.net}
\homepage{nullsum.net}
\social[github]{nvllsvm}

\begin{document}
\makecvtitle

\section{Experience}

\cventry[2em]{\dates[2022-07 2023-08]}{Gisual}{Senior Software Engineer}{}{}{{}
    \begin{itemize}
    \item \textbf{Technologies:} Python, RabbitMQ, PostgreSQL (with PostGIS, TimescaleDB), Redis, Kubernetes, Azure
    \item Designed an image-based captcha solver to enable product expansion into international locations serving one of our largest customers.
    \item Built an event-driven experimentation platform to vet the viability of using third-party data sources to augment the accuracy of the power diagnosis product.
    \item Led development of a system (web, HTTP, AMPQ) to empower a team to manually meet customer SLAs when the automated system cannot diagnose power.
    \item Reduced stack complexity and fixed long standing bugs by transitioning from a synchronous/asynchronous ecosystem to strictly asynchronous.
    \end{itemize}
}

\cventry[2em]{\datespresent[2018-12]}{Jellyfin - Open Source Media System}{Co-Founder}{}{}{{}
    \begin{itemize}
        \item \textbf{Technologies:} audio/video transcoding, C\#, Python, Docker
        \item Led initial development while ensuring documentation, build procedures/scripts, and artifacts are clearly defined for new developers looking to contribute.
        \item Strong influence over the project's branding (name, logo, colors) with an emphasis on brand recognition and accessibility to a broad user base.
        \item Built various related tools/applications which are used by the community including a Subsonic API proxy, tool to pre-transcode audio, and a standalone transcoding service.
    \end{itemize}
}

\cventry[2em]{\dates[2017-01 2022-07]}{AWeber}{Senior Software Engineer}{}{}{{}
    \begin{itemize}
    \item \textbf{Technologies:} Python, RabbitMQ, PostgreSQL, Redis, Kubernetes, GitLab, AWS
    \item Designed, developed, and supported solutions relating to email deliverability, content templating, and web push notifications.
    \item Built an event-driven platform for sending push notifications (web, Android, iOS) to our customers regarding subscriber updates and email analytics.
    \item Led development of AWeber's next-generation email templating engine which both simplified the internal stack and increased functionality for over 100,000 customers.
    \item Designed and implemented the backend for the public email archive hub.
    \item Regular contributor to AWeber's in-house and public-facing Python standards and libraries.
    \end{itemize}
}

\cventry[2em]{\dates[2015-07 2017-01]}{AWeber}{Application Support Engineer}{}{}{{}%
    \begin{itemize}
    \item \textbf{Technologies:} Python, PHP, RabbitMQ, PostgreSQL, JavaScript, Perl, Erlang
    \item Developed and supported a diverse ecosystem of technologies.
    \item Regularly worked across many parts of the stack (backend, frontend, database, operations).
    \item Triaged and resolved customer-facing issues.
    \item Designed and developed backend and frontend tools to aid both customers and fellow employees.
    \item Engaged with third-party AWeber API developers to provide guidance and support.
    \end{itemize}
}

\cventry[2em]{\dates[2012-05 2015-07]}{Associate Developer}{Guardian Life Insurance}{}{}{{}%
    \begin{itemize}
    \item \textbf{Technologies:} COBOL, SQL, DB2, C\#, Python
    \item Enhanced and supported existing mainframe insurance rating and renewal applications.
    \item Converted various group insurance renewal formula calculations from COBOL to Python.
    \item Led and coded DB2 optimization effort in an C\#/ASP.NET/mainframe system.
    \item Designed and developed automated DB2 stored procedure regression test framework (Python).
    \item Worked closely with the business to provide ad-hoc DB2 SQL reports.
    \item Authored and provided system requirements to offshore development teams.
    \end{itemize}
}

\section{Skills}
\cvlistitem {Python}
\cvlistitem {POSIX shell}
\cvlistitem {PostgreSQL / SQLite}
\cvlistitem {Redis}
\cvlistitem {HTTP}
\cvlistitem {AMQP / RabbitMQ / MQTT}
\cvlistitem {digital audio/images/video}
\cvlistitem {Linux}
\cvlistitem {Docker}
\cvlistitem {Kubernetes}
\cvlistitem {AWS}
\cvlistitem {Azure}


\nocite{*}
\bibliographystyle{plain}

\clearpage

%-----       letter       ---------------------------------------------------------

% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.
%
%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.
%
%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.
%
%Albert Einstein discovered that $e=mc^2$ in 1905.
%
%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
%
%\makeletterclosing
%
%%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}
%
%
%%% end of file `template.tex'.
